Tracing the Stellar Halo of Massive Galaxies to 100 kpc at $0.3<z<0.5$ using the Hyper Suprime-Cam

### 2017-05-25 draft/paper1_jenny.tex
Edit Appendix B

    In Section~\ref{ssec:isedfit}, we briefly explain the SED fitting procedure and 
    the priors used.   
    In Fig~\ref{fig:ised_1}, we show an example of the \texttt{iSEDFit} output by 
    visualizing the 5-band HSC SED on top of the best-fit model along with the PDF 
    of the key parameters. 
    Although we only use the best-fit \m2l{} in this work, it is necessary to make 
    sure the model is reasonable. 
    We show the relations between \mstar{} and a few key stellar population parameters 
    derived by \texttt{iSEDFit} in Fig~\ref{fig:ised_2}. 
    Although degeneracies among these parameters are almost inevitable using only 
    five broad-band photometry, most massive galaxies in both \rbcg{} (left) and 
    \nbcg{} (right) samples have old age, high metallicity ($1.5 \times Z_{\odot}$ is 
    the highest metallicity allowed by the adopted \texttt{FSPS} SSP models), and low 
    dust extinction as expected

    Meanwhile, \mstar{} measurement based on SED fitting heavily depends on the 
    adopted SSP model, the form of IMF, dust extinction law, and details in 
    the assumption of SFH (e.g.\ \citealt{Bernardi2016b}). 
    For massive galaxies in this sample, the form of the SFH\footnote{We choose 
    to use the delayed-$\tau$ model for SFH; we adopt flat distribution between 
    0.5 to 14.0 Gyrs as the prior for the look-back time when the star formation 
    turned on. 
    The exponential delayed time-scale ($\tau$) is allowed to change between 
    0.1 to 3.0 with equal probability}, the contribution from random star 
    burst\footnote{The chance of random star burst is set at 0.2 for every 2 Gyrs. 
    The duration of the star burst is draw from a logarithmic distribution 
    between 0.03 to 0.3 Gyr; and the mass fraction formed in the burst is from 
    a logarithmic distribution between 0.01 and 1.0.} do not affect the results. 
    On the other hand, the choices of SSP model, IMF, and dust extinction do impact
    the SED fitting results systematically, and we explore it using a few 
    additional tests (see Fig~\ref{fig:ised_3}):

@@

        \item Choosing the \citet{Salpeter1955} IMF results in systematically 
            higher \mstar{} (on average $+0.25$ dex of \logms{}) for both \rbcg{}
            and \nbcg{} galaxies (Left panels).
            Although there are multiple lines of evidence that favor Salpeter 
            or even more ``bottom-heavy'' IMF in massive galaxies 
            (e.g.\ \citealt{Conroy2012}; \citealt{Cappellari2012}), we still 
            present the main results using Chabrier IMF to accommodate galaxies 
            with lower \mstar{} in the sample, and to be as consistent as possible 
            with a few previous works.  
            This choice of IMF does not change the main results qualitatively.

        \item \mstar{} based on the \texttt{BC03} models are systematically lower 
            than the ones based on \texttt{FSPS+MILES} models (middle panels)
            The difference shows a large scatter, and can be as large as 0.4 dex,
            although it does show any \mstar{} dependency. 
            We notice that the \texttt{BC03} provides better overall ${\chi}^2$. 
            This could relates to the higher upper limit of stellar metallicity 
            ($2 \times \mathrm{Z}_{\odot}$) allowed by the \texttt{BC03} model 
            that help fit the shape of the SED in the red-end better.  
            However, the \texttt{BC03} model could underestimate the 
            stellar age for a fraction of massive galaxies ($< 3$--4 Gyrs), and 
            leads to underestimate of  \m2l{} for them too.
            It is worth noting that, both \texttt{FSPS} and \texttt{BC03} 
            models still have difficulties recovering SED at the red-end (between $z$ 
            and Y-band), and reproducing the optical color-color relations for 
            red-sequence galaxies (e.g.\ \citealt{MIUSCAT2}).
            In this work, we decide to keep using the \texttt{FSPS+MILES} model as 
            the fiducial one.  
            However, using the results based on \texttt{BC03} model will not 
            only change the main conclusions here, but also results in more 
            significant differences in the median \mden{} profiles.

        \item On the right panels of Fig~\ref{fig:ised_3}, we also compare with the
            SED fitting results without considering the dust extinction. 
            This choice leads to slightly smaller \mstar{} values as expected. 
            The impact is very small for the \rbcg{} galaxies, and becomes larger 
            at the low-\mstar{} end of the \nbcg{} sample. 
            But it still will not change any of the important results in this work.

>>>>

    In Section~\ref{ssec:isedfit}, we briefly explain the SED fitting procedure and 
    the priors used.   
    In Fig~\ref{fig:ised_1}, we show an example of the \texttt{iSEDFit} output by 
    visualizing the 5-band HSC SED on top of the best-fit model along with the PDF 
    of the key parameters.

    Although we only use the best-fit \m2l{} in this work, it is necessary to make 
    sure the model is reasonable. 
    We show the relations between \mstar{} and a few key stellar population parameters 
    derived by \texttt{iSEDFit} in Fig~\ref{fig:ised_2}. 
    Degeneracies among these parameters are inevitable based on only five broad-band
    photometry, but as expected, most massive galaxies show old stellar age, high
    stellar metallicity ($1.5 \times Z_{\odot}$ is the highest metallicity allowed by 
    the adopted \texttt{FSPS} SSP models), and low dust extinction.

    Meanwhile, \mstar{} measurement based on SED fitting heavily depends on the 
    adopted SSP model, the form of IMF, dust extinction law, and details in 
    the assumption of SFH (e.g.\ \citealt{Bernardi2016b}). 
    For massive galaxies in this sample, the form of the SFH\footnote{We choose 
    to use the delayed-$\tau$ model for SFH; we adopt flat distribution between 
    0.5 to 14.0 Gyrs as the prior for the look-back time when the star formation 
    turned on. 
    The exponential delayed time-scale ($\tau$) is allowed to change between 
    0.1 to 3.0 with equal probability}, the contribution from random star 
    burst\footnote{The chance of random star burst is set at 0.2 for every 2 Gyrs. 
    The duration of the star burst is draw from a logarithmic distribution 
    between 0.03 to 0.3 Gyr; and the mass fraction formed in the burst is from 
    a logarithmic distribution between 0.01 and 1.0.} rarely affect the \mstar{}. 
    But he choices of SSP model, IMF, and dust extinction do systematically impact
    the estimates of \mstar{}, and therefore we look into this with a few 
    additional tests (see Fig~\ref{fig:ised_3}):

@@

        \item Choosing the \citet{Salpeter1955} IMF results in systematically 
            higher \mstar{} (on average $+0.25$ dex of \logms{}) for these massive 
            galaxies (top panel).
            Although there are multiple lines of evidence that favor Salpeter 
            or even more ``bottom-heavy'' IMF in massive galaxies 
            (e.g.\ \citealt{Conroy2012}; \citealt{Cappellari2012}), we still 
            present the main results using Chabrier IMF to accommodate galaxies 
            with lower \mstar{} in the sample, and to be as consistent as possible 
            with previous works.  
            This choice of IMF does not change the main results qualitatively.

        \item \mstar{} based on the \texttt{BC03} models are systematically lower 
            than the ones based on \texttt{FSPS+MILES} models (middle panel)
            The difference shows a large scatter, and can be as large as 0.4 dex,
            although it is not \mstar{}-dependent. 
            The \texttt{BC03} results show better average ${\chi}^2$ than the 
            \texttt{FSPS} ones. 
            This relates to the higher upper-limit of stellar metallicity 
            ($2 \times \mathrm{Z}_{\odot}$) allowed by the \texttt{BC03} model, 
            which help fits the shape of the SED in the red-end slightly better.  
            However, the \texttt{BC03} results also show puzzlingly low stellar 
            ages ($< 3$--4 Gyrs) for these massive, red galaxies. 
            This could also lead to underestimated \m2l{} values.
            It is worth noting that, both \texttt{FSPS} and \texttt{BC03} 
            models still have difficulties recovering SED at the very red-end 
            (between $z$ and $y$-band), and reproducing the optical color-color 
            relations for red-sequence galaxies (e.g.\ \citealt{MIUSCAT2}).
            In this work, we decide to keep using the \texttt{FSPS+MILES} model as 
            the fiducial one.  
            Using results based on \texttt{BC03} model will not change any of our 
            conclusions here.

        \item On the bottom panel of Fig~\ref{fig:ised_3}, we compare with the
            SED fitting results without considering the dust extinction. 
            This choice leads to slightly smaller \mstar{} values as expected. 
            Its impact becomes slightly larger at lower \mstar{} end. 
            It will not change any of our conclusions here.
